Covariate analysis of UFL-Mayo-ISB RNASeq (both cerebellum and temporal cortex)

### 2016-05-16 code/Rmd/Mayo_RNASeq.Rmd
Added RIN2 to the Mayo pipeline

### Data preprocessing
```{r preprocess.data,cache=FALSE, echo=TRUE}
# Fix metadata
METADATA$AgeAtDeath = gsub("_or_above", "", METADATA$AgeAtDeath)
METADATA$Diagnosis = gsub("Pathologic Aging","Pathologic_Aging", METADATA$Diagnosis)
METADATA$BrainRegion.Diagnosis = paste(METADATA$BrainRegion, METADATA$Diagnosis, sep = '.')
METADATA <- METADATA %>%
  dplyr::filter(!(ID %in% c("742_CER", "11386_CER","11311_CER","1923_CER","11477_CER", "11344_CER", 
                            "1923_TCX", "11423_TCX", "1940_TCX", "7095_TCX", "11408_TCX")))
```
Following samples were considered outliers and removed based on PCA and/or eucledian distance:
```{r preprocess.data1}
# Match covariates to expression data
indToRetain = intersect(METADATA$ID, colnames(COUNT))

@@

### Covariate clustering
Determine relationship between covariates. 
```{r covariates.clustering}
FactorCovariates <- c("Donor_ID", "Source", "Gender", "FLOWCELL", "BrainRegion.Diagnosis")
ContCovariates <- c("RIN", "AgeAtDeath")

>>>>

### Data preprocessing
```{r preprocess.data,cache=FALSE, echo=TRUE}
# Fix metadata
METADATA$AgeAtDeath = gsub("_or_above", "", METADATA$AgeAtDeath)
METADATA$Diagnosis = gsub("Pathologic Aging","Pathologic_Aging", METADATA$Diagnosis)
METADATA$BrainRegion.Diagnosis = paste(METADATA$BrainRegion, METADATA$Diagnosis, sep = '.')
METADATA$RIN2 = METADATA$RIN^2
METADATA <- METADATA %>%
  dplyr::filter(!(ID %in% c("742_CER", "11386_CER","11311_CER","1923_CER","11477_CER", "11344_CER", 
                            "1923_TCX", "11423_TCX", "1940_TCX", "7095_TCX", "11408_TCX")))
```
Following samples were considered outliers and removed based on PCA and/or eucledian distance:
```{r preprocess.data1}
# Match covariates to expression data
indToRetain = intersect(METADATA$ID, colnames(COUNT))

@@

### Covariate clustering
Determine relationship between covariates. 
```{r covariates.clustering}
FactorCovariates <- c("Donor_ID", "Source", "Gender", "FLOWCELL", "BrainRegion.Diagnosis")
ContCovariates <- c("RIN", "RIN2", "AgeAtDeath")
